### 2019-04-19 VG500/Slide/tex/main.tex
add intro

\input{preamble.tex}
\input{pdfinfo.tex}
\input{title.tex}

@@

\section{Themes}

\subsection{Background images}

\begin{xframe}{Themes for the Elegance}

    You need a \hl{style/images} directory
    with these files inside:

    \begin{itemize}
        \item style/background-section.pdf
        \item style/background-slide.pdf
        \item style/background-title.pdf
        \item style/logo.png
    \end{itemize}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../pic/theme-1.png}}
\begin{frame}[plain]
    .
\end{frame}
}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../pic/theme-2.png}}
\begin{frame}[plain]
    .
\end{frame}
}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../pic/theme-3.png}}
\begin{frame}[plain]
    .
\end{frame}
}

\section{Examples}

@@

>>>>

\input{preamble.tex}
\input{title.tex}

@@

\section{Introduction}

	\subsection{part1.1}

		\begin{xframe}{Backgound}
			Turbulent combustion is encountered in most practical combustion system such as \textit{rocket}, \textit{ICE}, \textit{aircraft engien}, and \textit{industrial burner}.
			\begin{figure}[htbp]\centering
				\begin{minipage}{3.5cm}
					\centering
					\includegraphics[height=4.5cm, width=3cm]{../pic/rocket.jpg}
				\end{minipage}%
				\begin{minipage}{7.5cm}
					\centering
					\includegraphics[height=4.5cm, width=7cm]{../pic/engien.jpg}
				\end{minipage}%
			\end{figure}
		\end{xframe}

		\begin{xframe}{Research aspects}
			Meaningful to practical systems:
			\begin{enumerate}[(a)]
				\item 
					Improve efficiency, meet demanding standards.
				\item
					Reduce pollution, environment friendly.
			\end{enumerate}

			Why is numerical simulation adopted?
			\begin{enumerate}[(a)]
				\item 
				Analytical techniques are difficult to handle.
				\item
				Experiments are too expensive to be widely used.
			\end{enumerate}
		\end{xframe}

		\begin{xframe}{Physical Configuration}
			\includegraphics[width=7cm, height=8cm]{../pic/counterflow_configuration.png}	
		\end{xframe}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../pic/theme-2.png}}
\begin{frame}[plain]

\end{frame}
}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../pic/theme-3.png}}
\begin{frame}[plain]

\end{frame}
}

\section{Governing Equations}

@@

\section{Numerical Solution}
